\documentclass[12pt]{article}

%%% --- Package Imports --- %%%

\usepackage[table,xcdraw]{xcolor}
\usepackage{graphicx}
% Required for the tables


%%% --- DOCUMENT START --- %%%

\begin{document}

\section*{King's College London}
\vspace{-4mm}
\section*{Faculty of Social Science and Public Policy}
% Change this if you're in a different school
\vspace{-4mm}
\subsection*{Coversheet for submission of coursework}
\vspace{-3mm}
\subsection*{(Undergraduate \& Taught Postgraduate)}

\vspace{+5mm}

\section*{DECLARATION BY STUDENT}
This assignment is entirely my own work. Quotations from secondary literature are indicated by the use of inverted commas around ALL such quotations AND by reference in the text or notes to the author concerned.  ALL primary and secondary literature used in this piece of work is indicated in the bibliography placed at the end, and dependence upon ANY source used is indicated at the appropriate point in the text.  I confirm that no sources have been used other than those stated. 
\linebreak

\textbf{I understand what is meant by plagiarism and have signed at enrolment the declaration concerning the avoidance of plagiarism.}

\textbf{I understand that plagiarism is a serious examinations offence that may result in disciplinary action being taken.}

\textbf{I understand that I must submit work BEFORE the deadline, and that failure to do so will result in capped marks.}

\begin{table}[h]
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|l|l|l|l|}
\hline
% CANDIDATE NUMBER GOES HERE
Candidate no. & \begin{tabular}[c]{@{}l@{}}A\\ B\end{tabular} & X & X & X & X & X & X \\ \hline
\end{tabular}
\end{table}

% You can use https://www.tablesgenerator.com to generate the tex code for new tables if the below ones don't look good for your module title.

\begin{table}[h]
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|}
% If your module title is very long replace the above "l" with p{.7\linewidth} which will cap the max width of the table cell to 70% of the length of the line and enable text wrapping
\hline
Module Title: & Some Random Module Title Goes Here\\ \hline
Module Code:  & \multicolumn{1}{c|}{9XXXX999}                                                          \\ \hline
\end{tabular}
\end{table}

\begin{table}[h]
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |c|}
\hline
Assignment        & Some Assignment Title Goes Here  \\ \hline
Assignment Tutor: & Dr Someone Someone               \\ \hline
Deadline          & 01/01/1970                       \\ \hline
Date Submitted    & 01/01/1970                       \\ \hline
Word Count        & 1337                             \\ \hline
\end{tabular}
\end{table}


% Change this if you don't mind your work being used as an example in the future
I \textbf{DO NOT} consent to my assignment being used  as an example of good practice for other students to refer to in future.

\end{document}
